---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(benchlingapi)

# mock for the sake of output
get_users <- function() {
structure(list(email = c("jamey@example.com", "peggy@example.com", 
"gabriel@example.com", "felix@example.com", "garett@example.com"), handle = c("jamey", "peggy", "gabriel", "felix", 
"garett"), id = c("ent_SPXdAvAd", "ent_N3ARMuA4", 
"ent_og8mNFAy", "ent_CXxJcHK2", "ent_qac9DiQn"), name = c("Jamey Olson", "Peggy Paucek", "Gabriel Toy", 
"Felix Rohan", "Garett Donnelly")), row.names = c(NA, 
5L), class = "data.frame")
}
```

# benchlingapi

<!-- badges: start -->
<!-- badges: end -->

Connect to the benchling API via R.

## Installation

You can install the development version of benchlingapi like so:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("HIBio/benchlingapi")

library(benchlingapi)
```

## Authentication

Set up the following environment variables for easy access (e.g. using `usethis::edit_r_environ()`)

``` bash
BENCHLING_ORG=yourorgname
BENCHLING_TOKEN=sk_dMAQaaa9AaAAwwADRAzAs2AAz4Aaa
```

## Configuration

`set_creds()` can be used to validate and set the credentials for a given tenant 
(itself set via `BENCHLING_ORG`). To switch between a fixed list of tenants, one 
could write a helper 

```{r, eval = FALSE}
use_tenant <- function(tenant = c("test", "prod")) {
  tenant <- match.arg(tenant)
  message("switching to ", tenant)
  switch(tenant,
         prod = benchlingapi::set_creds(
           org_var = "PROD_BENCHLING_ORG",
           token_var = "PROD_BENCHLING_TOKEN"
         ),
         # default
         test = benchlingapi::set_creds()
  )
  invisible()
}
```

This has *not* been included in {benchlingapi} as organisations may have their own list of tenants to 
configure.

## Example

```{r}
get_users()
```

## Supported Endpoints

Most of the endpoints have been automatically wrapped[^inst] but there is no guarantee that they work.

The endpoints which should be wrapped with a `get_*` function are
```{r, echo = FALSE}
sub(".R$", "", sub("^auto_", "", dir("R", pattern = "auto_*")))
```

Some of these take an additional (optional) parameter (only one supported for now), e.g.

```{r}
benchlingapi::get_users
```

Many endpoints also include query parameters (see the [official reference](https://benchling.com/api/reference)).
These can be specified via the `...` argument, and are detailed in the individual help for each function, e.g.

```{r, eval = FALSE}
?get_users
```

----

```{r, echo = FALSE, results='asis'}
help_console <- function(topic, package,
                         format=c("text", "html", "latex", "Rd"),
                         before=NULL, after=NULL) {
  # topic - the command for which help is required
  # package - the package name with the required topic
  # format - output format
  # before - place code before the output e.g. "<blockquote>"
  # after - place code after the output e.g. "</blockquote>"

  # based on code by Noam Ross
  #  http://www.noamross.net/archives/2013-06-18-helpconsoleexample/
  # Stéphane Laurent
  #  https://stackoverflow.com/questions/60468080/
  #   print-an-r-help-file-vignette-as-output-into-an-r-html-notebook
  # and Michael Sumner (mdsumner)
  #  https://stackoverflow.com/questions/7495685/
  #   how-to-access-the-help-documentation-rd-source-files-in-r

  format <- match.arg(format)
  if (!is.character(topic)) topic <- deparse(substitute(topic))
  db <- tools::Rd_db(package)
  helpfile <- db[paste0(topic, ".Rd")][[1]]

  hs <- capture.output(
    switch(
      format,
      text = tools::Rd2txt(helpfile),
      html = tools::Rd2HTML(
        helpfile,
        package = "",
        stages = c("install", "render")
      ),
      latex = tools::Rd2latex(helpfile),
      Rd = tools:::prepare_Rd(helpfile)
    )
  )
  if (format == "html") {
    i <- grep("<h2>", hs)
    j <- grep("</body>", hs)
    hs <- hs[(i-1):(j-1)]
  }
  hs <- c(before, hs, after)
  hs <- cat(hs, sep = "\n")
  invisible(hs)
}

help_console("users", "benchlingapi", format = "html")
```

----

As an example, if your users list has several users with the name 'David'

```{r, eval = FALSE}
get_users(nameIncludes = "david")
```
```{r, echo = FALSE}
structure(list(email = c("david.old@example.com", "david.new@example.com"
), handle = c("david.old", "david.new"), id = c("ent_U2gA6a41", "ent_AvA2sA2X"
), name = c("David Old", "David New")), class = "data.frame", row.names = 1:2)
```

# Logging

{benchlingapi} uses [{logger}][logger] for logging messages, warnings, errors, and 
debug info. A default of `logger::log_threshold(ERROR)` is set on package load, but 
can be overridden, e.g.

```{r, eval = FALSE}
logger::log_threshold(DEBUG)
get_users(nameIncludes = "david")
```
```
DEBUG [2023-03-27 16:53:25] GET prod with endpoint: users
DEBUG [2023-03-27 16:53:25] Building query from `...` arguments
DEBUG [2023-03-27 16:53:25] query to be sent: list(nameIncludes = "david")
SUCCESS [2023-03-27 16:53:26] Returned status code: 200
```
```{r, echo = FALSE}
structure(list(email = c("david.old@example.com", "david.new@example.com"
), handle = c("david.old", "david.new"), id = c("ent_U2gA6a41", "ent_AvA2sA2X"
), name = c("David Old", "David New")), class = "data.frame", row.names = 1:2)
```
Errors and messages can be injected with `logger::log_errors()` and 
`logger::log_messages()`.

[^inst]: See `inst/scripts/template.R` for how these `auto_*.R` files are generated

[logger]: https://daroczig.github.io/logger/index.html
