---
title: "Usage Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  purl = FALSE
)
```

## Overview

This vignette provides some more detailed examples of how to use the Benchling
API using this package.

Currently you must have two environment variables set to enable API access, you
can choose what to name them but the default names are:

1. `BENCHLING_ORG`: The is the subdomain in the `subdomain.benchling.com` that
   you are using to access your benchling tenant.
2. `BENCHLING_TOKEN`: This is the API key you will use to query Benchling. This
   is generated on a per-user basis within benchling by an admin.

Whatever they are, provide the appropriate variable names to the `set_creds`
function to set them internally. I have two pairs of environment variables set,
a pair to keep the auth credentials for our test tenant, and another pair for
the production tenant, so my call to `set_creds()` will look like:

```{r}
# library(benchlingapi)
devtools::load_all(".")
set_creds("BENCHLING_PROD_ORG", "BENCHLING_PROD_TOKEN")
```

After the usual R package installation, `torch` requires installing other 2 libraries: LibTorch and LibLantern. They are automatically installed by detecting information about you OS if you are using `torch` in interactive mode. If you are running `torch` in non-interactive environments you need to set the `TORCH_INSTALL` env var to 1, so it's automatically installed or manually call `torch::install_torch()`.

We have provide pre-compiled binaries for all major platforms and you can find specific installation instructions below.

## Windows

### CPU

If you don't have a GPU or want to install the CPU version of `torch`, you can install with:

```{r, eval = FALSE}
install.packages("torch")
```
