---
title: "Usage Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  purl = FALSE
)
```

## Overview

This vignette provides some more detailed examples of how to use the Benchling
API using this package.

Currently you must have two environment variables set to enable API access, you
can choose what to name them but the default names are:

1. `BENCHLING_ORG`: The is the subdomain in the `subdomain.benchling.com` that
   you are using to access your benchling tenant.
2. `BENCHLING_TOKEN`: This is the API key you will use to query Benchling. This
   is generated on a per-user basis within benchling by an admin.

Whatever they are, provide the appropriate variable names to the `set_creds`
function to set them internally. I have two pairs of environment variables set,
a pair to keep the auth credentials for our test tenant, and another pair for
the production tenant, so my call to `set_creds()` will look like:

```{r}
# library(benchlingapi)
devtools::load_all(".")
set_creds("BENCHLING_PROD_ORG", "BENCHLING_PROD_TOKEN", validate = TRUE)
```

The `validate = TRUE` argument above makes a quick call to the benchling tenant
to ensure that the credentials work -- if they don't, the function will throw
an error.

