---
title: "Usage Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  purl = FALSE
)
```

## Configuration

This vignette provides some more detailed examples of how to use the Benchling
API using this package.

Currently you must have two environment variables set to enable API access, you
can choose what to name them but the default names are:

1. `BENCHLING_ORG`: The is the subdomain in the `subdomain.benchling.com` that
   you are using to access your Benchling tenant. Some configurations include a 
   'test' tenant and a 'production' tenant.
2. `BENCHLING_TOKEN`: This is the API key you will use to query Benchling. This
   is generated on a per-user basis within Benchling by an admin.

Whatever they are, provide the appropriate variable names to the `set_creds()`
function to set them internally. I have two pairs of environment variables set,
a pair to keep the auth credentials for our test tenant, and another pair for
the production tenant, so my call to `set_creds()` will look like:

```{r}
library(benchlingapi)
set_creds("BENCHLING_PROD_ORG", "BENCHLING_PROD_TOKEN", validate = TRUE)
```

The `validate = TRUE` argument above makes a quick call to the Benchling tenant
to ensure that the credentials work -- if they don't, the function will throw
an error.

With this set up, queries to the Benchling API should not require passing around tokens.

## Query the API

The [API reference](https://benchling.com/api/reference) details the endpoints, 
query parameters, and expected response schema. A similar reference is typically 
available for each specific installation/tenant as 
\url{https://TENANT.benchling.com/api/reference#/}. 

{benchlingapi} wraps most of the direct `GET` endpoints with a similar `get_x()` 
function, exposing the optional query parameters via the `...` argument. When such 
a query offers specific fetching of an entity via an ID this is exposed as a named
argument, e.g. `get_aa_sequences(aa_sequence_id)`. The help pages are auto-generated
from the API reference and detail the optional query parameters. Use e.g. `?get_aa_sequences` 
to see such documentation.

Some `POST` and `PATCH` functions are also wrapped. 

## Pagination

By default, the query parameter `pageSize` is set to 50 with a maximum of 100. If you require 
more results then set the `pageSize` argument to your desired upper limit. The query 
will be sent and a `nextToken` will be retrieved. A new search will be performed 
until the desired number of results is either collected or the search is exhausted.
